Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-28 paper/main.tex
add comment regarding Fig S1
some typos

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures is also present under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump''
\citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{hausler2021studyforrest}.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets with
BOLD fMRI data from naturalistic and conventional block-design stimulation from
the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
% pictures -> movie -> audio-description
The movie, as an intermediate step, offered a more naturalistic but still visual
stimulation whereas the audio-description, as a further step, offered a more
naturalistic but non-visual, semantic stimulation.
% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a conventional visual localizer
for each individual, because all three operationalization capitalize on events
that should evoke the cognitive processing of spatial information.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

@@

% traditionally
In contrast to stimuli designed to trigger a perceptual process of interest,
while controlling for confounding variables (e.g., color and luminance),
% our approach: annotation and regressors
naturalistic stimuli have fixed but initially unknown temporal structure of
stimulus features of interest, as well as an equally unknown confound structure.
% annotation ftw
In order to evaluate the suitability of the stimulus for the targeted analyses,
and well as to inform the required hemodynamic models, we annotated the temporal
structure of a range of stimulus features.

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% we focus on cuts
Contrary to manually annotating stimulus features of every movie frame (as
performed by e.g. \cite{bartels2004mapping} for color, faces, language, and
human bodies), we categorized movie cuts that - in general - realign the viewer
within the movie environment by switching to another perspective within the
same setting, or to a position in an entirely different setting.
% this this should work
More specifically, we sought to exploit a cinematographic bias as
% establishing shots & shots within setting early in the movie
at a setting's first occurrence in a movie, shots tend to broadly establish the
setting and the spatial layout within the setting.
% cut to recurrent scene
On revisiting an already established setting, the field sizes of movie shots
tend to decrease, and shots tend to more often depict people talking to each
other or objects that are relevant to the evolved plot
\citep{brown2012cinematography, katz1991film, mascelli1998five}.

@@

% AV regressors/events
Based on this cinematographic bias, we assigned each cut to one of five
categories (Tab.~\ref{tab:events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro
As a control condition with events of no particular processing of spatial
information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
continuous movie shots that lasted longer than \unit[20]{s}, and
% no cuts: how
had a minimum temporal distance of at least \unit[10]{s} to any movie cut and to
any other \texttt{no\_cut} event.

@@

    Event categories of the audio-description based on an annotation of nouns
    spoken by the audio-description's narrator

@@

    Respective event counts are given for the whole stimulus (\texttt{All} and
    the segments that were used for the eight sessions of fMRI scanning).

@@

\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
these? COH: no clue what to do with that feedback}
% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
Maximum correlations are found for auditory low-level auditory confounds across
stimuli,
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
between root mean square volume of both audio tracks, r=.76; correlation between
left-right volume difference of both audio tracks, r=.77).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.

@@

% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and
rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

% there isn't "the one road"
Given the rich naturalistic stimuli and the availability of various stimulus
feature annotations, there are several candidates for implementing contrasts to
identify hemodynamic activity congruent with the hypothesized processing of
spatial information in the PPA.
% kind of arbitrary choice
However, while the rationale for any contrast composition must be sound, the
selection of a single implementation remains arbitrary to some degree.
% hence, a couple of contrasts
Consequently, we computed multiple contrasts that are listed in
Table~\ref{tab:contrasts} for movie and audio-description, respectively.
% subjectively assessed balance
For each stimulus, we picked a primary contrast for result presentation (the
first one in each Table) based on a subjectively assessed balance of how well
the average event within categories represents spatial and non-spatial
information, and the number of events in the stimulus.
% reference to supplementals
An evaluation of the robustness of these results with respect to similar but
different contrasts is provided in the supplementary materials.

% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with nouns referring to a person's
head or face (\texttt{fahead}), and other non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) they comprise nouns that could be a member of another category (e.g. ``[a]
physician''), and
% richness of verbal description vs. picture
b) nouns that only vaguely identify a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') compared to perceptually richer
descriptions.

% control contrasts
Finally, we created several control contrasts for both stimuli
(Tab.~\ref{tab:contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut}) to cut-related regressors.
% AV: narrator
One contrast was created by contrasting nouns spoken by the (missing) narrator
comparing nouns that indicate a switch to another setting (\texttt{se\_new} >
\texttt{se\_old}), and were moderately correlated with movie cuts indicating a
switch to another setting (Tab.~\ref{fig:reg-corr}).
% AD stimulus
For the audio-description stimulus, we created five control contrasts to test if
activation in the PPA was correlated with moments of cuts, despite the absence
of visual stimulation.

@@

% table group results primary AD contrast
\begin{table*}[tbp]
\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-description comparing
    geometry-related nouns to non geometry-related nouns spoken by the
    audio-description's narrator (\texttt{geo, groom > all non-geo}), sorted by size.
    The first brain structure given contains the voxel with the maximum $Z$-value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l.: left; r: right; c.: cortex; g.: gyrus; CoG: Center of
    Gravity).}
    \label{tab:res-ao-group1}
\small
\begin{tabular}{rrrrrrrrrp{4.7cm}}
\toprule
& & & \multicolumn{3}{r}{Max (MNI)} & \multicolumn{3}{r}{CoG (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
Voxels & $p_{corr.}$ & $Z_{max}$ & X & Y & Z  & X & Y & Z & Structure \\
\midrule
188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.~precuneus \\ % 0.0000000596
164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r.~precuneus;
\\ % 0.000000238
83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r.~occipito-temporal fusiform c.; posterior parahippocampal g. \\ % 0.000128
73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l.~lingual
g.; occipito-temporal fusiform g., posterior parahippocampal c. \\ % 0.000128
63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r.~superior
lateral occipital c. \\ % 0.000824
37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l.~superior
lateral occipital c. \\ % 0.0129
\bottomrule
\end{tabular}
\end{table*}

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
clusters in two participants \citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for each
naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary
movie and audio-description $t$-contrasts, in comparison to the results of a
conventional block-design localizer (unthresholded $Z$-maps are provided on
NeuroVault).
% AV
Results of the primary movie contrast yielded bilateral clusters in five
participants, a unilateral right cluster in six participants (of which one
participant yielded a unilateral cluster in the visual localizer), and a
unilateral left cluster in one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the
block-design localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in
nine participants that are within or overlapping with the block-design localizer
results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in
the left-hemispheric PPA.

@@

% shortcomings
%#2
Our approach to stimulus annotation and event selection differs from previous
reports in the literature.
% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% results
The group results of the movie stimulus' primary contrast yielded a large
cluster that spans the group overlap of individual PPA ROIs from anterior to
posterior.
% confound of higher perception
The cluster extends into more posterior, earlier visual areas could be an
indication that the temporal averaging across events suffered from insufficient
controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g.,
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

@@

%#13 natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} can be used as a continuous, complex,
immersive, task-free paradigm that more closely resembles our natural dynamic
environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an
auditory narrative, and compare current results to a previous report of a
conventional, block-design localizer.
% results
The current study offers evidence that a model-driven GLM analysis based on
annotations can be applied to naturalistic paradigm to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide further evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual scenes.
% interpretation
Finally, the presented evidence on the in-principle suitability of a naturally
engaging, purely auditory paradigm for localizing the PPA may offer a path to
the development of diagnostic procedures more suitable for individuals with
visual impairments or conditions like nystagmus.

@@

@@

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
order to test XYZ.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{not PPA! explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
%
\todo[inline]{concluding statement?}.

>>>>

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures is also present under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump''
\citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{hausler2021studyforrest}.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets with
BOLD fMRI data from naturalistic and conventional block-design stimulation of
the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
% pictures -> movie -> audio-description
The movie, as an intermediate step, offered a more naturalistic but still visual
stimulation whereas the audio-description, as a further step, offered a more
naturalistic but non-visual, semantic stimulation.
% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a conventional visual localizer
for each individual, because all three operationalization capitalize on events
that should evoke the cognitive processing of spatial information.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

@@

% traditionally
In contrast to stimuli designed to trigger a perceptual process of interest,
while controlling for confounding variables (e.g., color and luminance),
% our approach: annotation and regressors
naturalistic stimuli have a fixed but initially unknown temporal structure of
stimulus features of interest, as well as an equally unknown confound structure.
% annotation ftw
In order to evaluate the suitability of the stimulus for the targeted analyses,
and to inform the required hemodynamic models, we annotated the temporal
structure of a range of stimulus features.

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% we focus on cuts
Contrary to manually annotating stimulus features of movie frames (as
performed by e.g. \cite{bartels2004mapping} for color, faces, language, and
human bodies), we categorized movie cuts that - in general - realign the viewer
within the movie environment by switching to another perspective within the
same setting, or to a position in an entirely different setting.
% this this should work
More specifically, we sought to exploit a cinematographic bias as
% establishing shots & shots within setting early in the movie
at a setting's first occurrence in a movie, shots tend to broadly establish the
setting and the spatial layout within the setting.
% cut to recurrent scene
On revisiting an already established setting, the field sizes of movie shots
tend to decrease, and shots tend to more often depict people talking to each
other or objects that are relevant to the evolved plot
\citep{brown2012cinematography, katz1991film, mascelli1998five}.

@@

% AV regressors/events
Based on this cinematographic bias, we assigned each cut to one of five
categories (Tab.~\ref{tab:events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from the first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro
As a control condition with events of no particular processing of spatial
information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
continuous movie shots that lasted longer than \unit[20]{s}, and
% no cuts: how
had a minimum temporal distance of at least \unit[10]{s} to any movie cut and to
any other \texttt{no\_cut} event.

@@

    Event categories of the audio-description are based on an annotation of
    nouns spoken by the audio-description's narrator

@@

    Respective event counts are given for the whole stimulus (\texttt{All}) and
    the segments that were used for the eight sessions of fMRI scanning.

@@

\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
these? COH: no clue what to do with that feedback}
% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
Maximum correlations are found for low-level auditory confounds across
stimuli,
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
between root mean square volume of both audio tracks, r=.76; correlation between
left-right volume difference of both audio tracks, r=.77).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.

@@

% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimates (translation and
rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

% there isn't "the one road"
Given the rich naturalistic stimuli and the availability of various stimulus
feature annotations, there are several candidates for implementing contrasts to
identify hemodynamic activity congruent with the hypothesized processing of
spatial information in the PPA.
% kind of arbitrary choice
However, while the rationale for any contrast composition must be sound, the
selection of a single implementation remains arbitrary to some degree.
% hence, a couple of contrasts
Consequently, we computed multiple contrasts that are listed in
Table~\ref{tab:contrasts} for the movie and audio-description, respectively.
% subjectively assessed balance
For each stimulus, we picked a primary contrast for result presentation (the
first one in each Table) based on a subjectively assessed balance of how well
the averaged events within categories represent spatial and non-spatial
information, and the number of events in the stimulus.
% reference to supplementals
An evaluation of the robustness of these results with respect to similar but
different contrasts is provided in the supplementary materials.

% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with nouns referring to a person's
head or face (\texttt{fahead}), and other non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because they
comprise
% heterogeneous category
a)  nouns that could be a member of another category (e.g. ``[a]
physician''), and
% richness of verbal description vs. picture
b) nouns that only vaguely identify a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') compared to perceptually richer
descriptions.

% control contrasts
Finally, we created several control contrasts for both stimuli
(Tab.~\ref{tab:contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut}) to cut-related regressors.
% AV: narrator
One contrast was created by contrasting nouns spoken by the (missing) narrator
comparing nouns
%
that indicate a switch to another setting (\texttt{se\_new} >
\texttt{se\_old}), and
%
that were moderately correlated with movie cuts indicating a
switch to another setting (Tab.~\ref{fig:reg-corr}).
% AD stimulus
For the audio-description stimulus, we created five control contrasts to test if
activation in the PPA was correlated with moments of cuts, despite the absence
of visual stimulation.

@@

% table group results primary AD contrast
\begin{table*}[tbp]
\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-description comparing
    geometry-related nouns to non-spatial nouns spoken by the
    audio-description's narrator (\texttt{geo, groom > all non-geo}), sorted by size.
    The first brain structure given contains the voxel with the maximum $Z$-value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l.: left; r: right; c.: cortex; g.: gyrus; CoG: Center of
    Gravity).}
    \label{tab:res-ao-group1}
\small
\begin{tabular}{rrrrrrrrrp{4.7cm}}
\toprule
& & & \multicolumn{3}{r}{Max (MNI)} & \multicolumn{3}{r}{CoG (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
Voxels & $p_{corr.}$ & $Z_{max}$ & X & Y & Z  & X & Y & Z & Structure \\
\midrule
188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.~precuneus \\ % 0.0000000596
164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r.~precuneus;
\\ % 0.000000238
83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r.~occipito-temporal fusiform c.; posterior parahippocampal g. \\ % 0.000128
73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l.~lingual
g.; occipito-temporal fusiform g., posterior parahippocampal c. \\ % 0.000128
63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r.~superior
lateral occipital c. \\ % 0.000824
37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l.~superior
lateral occipital c. \\ % 0.0129
\bottomrule
\end{tabular}
\end{table*}

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
clusters in two participants \citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for each
naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary
movie and audio-description $t$-contrasts, in comparison to the results of a
conventional block-design localizer (unthresholded $Z$-maps are provided at
NeuroVault).
% AV
Results of the primary movie contrast yielded bilateral clusters in five
participants, a unilateral right cluster in six participants (of which one
participant yielded a unilateral cluster in the visual localizer), and a
unilateral left cluster in one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the
block-design localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in
nine participants that are within or overlapping with the block-design localizer
results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in
the left-hemispheric PPA.

@@

% shortcomings
%#2
Our approach to stimulus annotation and event selection differs from previous
reports in the literature.
% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
movie frames (color, faces, language, and human bodies) and found that the
functional specialization of brain areas is preserved during movie watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% results
The group results of the movie stimulus' primary contrast yielded a large
cluster that spans the group overlap of individual PPA ROIs from anterior to
posterior.
% confound of higher perception
The cluster extends into more posterior, earlier visual areas could be an
indication that the temporal averaging across events suffered from insufficient
controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g.,
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

@@

%#13 natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} can be used as a continuous, complex,
immersive, task-free paradigm that more closely resembles our natural dynamic
environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded in an audio-visual movie and an
auditory narrative, and compare current results to a previous report of a
conventional, block-design localizer.
% results
The current study offers evidence that a model-driven GLM analysis based on
annotations can be applied to a naturalistic paradigm to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual scenes.
% interpretation
Finally, the presented evidence on the in-principle suitability of a naturally
engaging, purely auditory paradigm for localizing the PPA may offer a path to
the development of diagnostic procedures more suitable for individuals with
visual impairments or conditions like nystagmus.

@@

\todo[inline]{I manually adjusted the stability-slices.pdf; the Fig S1 should
now (not just on my computer) show a black bar in the color maps for the
audio-descriptions (because there are 5 and not 8 contrasts)}

@@

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
order to test XYZ.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{not PPA! explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
%
\todo[inline]{concluding statement?}
